---
output: html_document
editor_options: 
  chunk_output_type: console
---
Red Wine Analysis by M. McIlvride
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# install.packages('ggplot2')
# install.packages('GGally')
# install.packages('gridExtra')
# install.packages('dplyr')

library(ggplot2)
library(GGally)
library(gridExtra)
library(tidyr)
library(purrr)
library(dplyr)
```

```{r echo=FALSE, Load_the_Data}
df <- read.csv('wineQualityReds.csv')

# create a new dataframe without outliers
df2 <- subset(df,
              alcohol < quantile(alcohol,
                                 probs = 0.99) &
              sulphates < quantile(sulphates,
                                   probs = 0.99) &
              total.sulfur.dioxide < quantile(total.sulfur.dioxide,
                                              probs = 0.99) &
              free.sulfur.dioxide < quantile(free.sulfur.dioxide,
                                             probs = 0.99) &
              chlorides < quantile(chlorides,
                                   probs = 0.99) &
              residual.sugar < quantile(residual.sugar,
                                        probs = 0.99) &
              citric.acid < quantile(citric.acid,
                                     probs = 0.99) &
              volatile.acidity < quantile(volatile.acidity,
                                          probs = 0.99) &
              fixed.acidity < quantile(fixed.acidity,
                                       probs = 0.99))

# remove the label column
df2 <- subset(df2, select = -c(X))
```

# Introduction
There is a lot of junk science about what makes a good wine. This analysis will
use data to draw conclusions about what really makes a good red wine.

# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Boxplots}
df2 %>%
  gather() %>%
  ggplot(aes(x = '', y = value)) +
    facet_wrap(~ key, scales = "free") +
    geom_boxplot()
```

A quick look at a boxplot matrix of our data shows that our data is generally
skewed right. We can also see that some of our variables, like chlorides and
residual sugar, have very low spread and many outliers. Viewing the data in this
way helps us see what sort of units each variable uses.

```{r echo=FALSE, message=FALSE, warning=FALSE, Quality}
ggplot(aes(x = factor(quality)),
       data = df2) +
  geom_bar() +
  labs(title = "Red Wines by Quality",
       x = "Quality",
       y = "Count")
```

The quality of the wines has a fairly normal distribution. The average wine has
a quality of 5.64. Later, we will perform more advanced analysis to find out
what factors contribute to a high quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Alcohol}
alcohol <-
  ggplot(data = df2,
         aes(x = alcohol)) +
    geom_histogram() +
    labs(title = "Red Wines by Alcohol Content",
         x = "Alcohol (% by volume)",
         y = "Count")

alcohol_log10 <-
  ggplot(data = df2,
         aes(x = alcohol)) +
    geom_histogram() +
    labs(title = "Red Wines by Alcohol Content (log10)",
         x = "Alcohol (% by volume)",
         y = "Count") +
    scale_x_log10()

grid.arrange(alcohol, alcohol_log10, ncol = 1)
```

The alcohol content of red wine is skewed right; the average bottle of red wine
is 10.42% alcohol but it can be as high as 14.9%.

```{r echo=FALSE, message=FALSE, warning=FALSE, Sulphates}
sulphates <-
  ggplot(data = df2,
         aes(x = sulphates)) +
    geom_histogram() +
    labs(title = "Red Wines by Sulphates",
         x = "Sulphates (potassium sulphate - g / dm3)",
         y = "Count")

sulphates_log10 <-
  ggplot(data = df2,
       aes(x = sulphates)) +
  geom_histogram() +
  labs(title = "Red Wines by Sulphates (log10)",
       x = "Sulphates (potassium sulphate - g / dm3)",
       y = "Count") +
  scale_x_log10()

grid.arrange(sulphates, sulphates_log10)
```

The sulphate content of red wine is also skewed heavily right. The average
bottle of red wine has a sulphate level of 0.66 but the highest level is 2.

```{r echo=FALSE, message=FALSE, warning=FALSE, pH}
qplot(data = df,
      x = pH,
      main = "Red Wines by pH",
      xlab = "pH",
      ylab = "Count")
```

The pH levels for red wine are normally distributed with an average pH level of
3.31.

```{r echo=FALSE, message=FALSE, warning=FALSE, density}
qplot(data = df,
      x = density,
      main = "Red Wines by Density",
      xlab = "Density (g / cm^3)",
      ylab = "Count")
```

The density of red wine is also normally distributed with an average density of
0.97.

```{r echo=FALSE, message=FALSE, warning=FALSE, Total_Sulfur_Dioxide}
total.sulfur.dioxide <-
  ggplot(data = df2,
         aes(x = total.sulfur.dioxide)) +
    geom_histogram() +
    labs(title = "Red Wines by Total Sulfur Dioxide",
         x = "Total Sulfur Dioxide (mg / dm^3)",
         y = "Count")

total.sulfur.dioxide_log10 <-
  ggplot(data = df2,
         aes(x = total.sulfur.dioxide)) +
    geom_histogram() +
    labs(title = "Red Wines by Total Sulfur Dioxide (log10)",
         x = "Total Sulfur Dioxide (mg / dm^3)",
         y = "Count") +
  scale_x_log10()

grid.arrange(total.sulfur.dioxide, total.sulfur.dioxide_log10, ncol = 1)
```

Total sulfur dioxide for red wine is skewed right with an average of 46.47.

```{r echo=FALSE, message=FALSE, warning=FALSE, Free_Sulfur_Dioxide}
qplot(data = df,
      x = free.sulfur.dioxide,
      main = "Red Wines by Free Sulfur Dioxide",
      xlab = "Free Sulfur Dioxide (mg / dm^3)",
      ylab = "Count")

free.sulfur.dioxide <-
  ggplot(data = df2,
         aes(x = free.sulfur.dioxide)) +
    geom_histogram() +
    labs(title = "Red Wines by Free Sulfur Dioxide",
         x = "Free Sulfur Dioxide (mg / dm^3)",
         y = "Count")

free.sulfur.dioxide_log10 <-
  ggplot(data = df2,
         aes(x = free.sulfur.dioxide)) +
    geom_histogram() +
    labs(title = "Red Wines by Free Sulfur Dioxide (log10)",
         x = "Free Sulfur Dioxide (mg / dm^3)",
         y = "Count") +
  scale_x_log10()

grid.arrange(free.sulfur.dioxide, free.sulfur.dioxide_log10, ncol = 1)
```

Free sulfur dioxide is similarly shaped to total sulfur dioxide, but with a
much lower average of 15.87.

```{r echo=FALSE, message=FALSE, warning=FALSE, Chlorides}
chlorides <-
  ggplot(data = df2,
         aes(x = chlorides)) +
    geom_histogram() +
    labs(title = "Red Wines by Chlorides",
         x = "Chlorides (sodium chloride - g / dm^3)",
         y = "Count")

chlorides_log10 <-
  ggplot(data = df2,
         aes(x = chlorides)) +
    geom_histogram() +
    labs(title = "Red Wines by Chlorides (log10)",
         x = "Chlorides (sodium chloride - g / dm^3)",
         y = "Count") +
  scale_x_log10()

grid.arrange(chlorides, chlorides_log10, ncol = 1)
```

The data for chlorides in red wine is heavily skewed left and has a very long
tail. While the mean chloride count is 0.09, the median is 0.08 due to the long
tail. The maximum value here is a massive 0.61.

```{r echo=FALSE, message=FALSE, warning=FALSE, Residual_Sugar}
residual.sugar <-
  ggplot(data = df2,
         aes(x = residual.sugar)) +
    geom_histogram() +
    labs(title = "Red Wines by Residual Sugar",
         x = "Residual Sugar (g / dm^3)",
         y = "Count")

residual.sugar_log10 <-
  ggplot(data = df2,
         aes(x = residual.sugar)) +
    geom_histogram() +
    labs(title = "Red Wines by Residual Sugar (log10)",
         x = "Residual Sugar (g / dm^3)",
         y = "Count") +
  scale_x_log10()

grid.arrange(residual.sugar, residual.sugar_log10, ncol = 1)
```

The data on residual sugar is very similar to the data on chlorides. The
residual sugars in red wine have an average of 2.54 and a max of 15.5.

```{r echo=FALSE, message=FALSE, warning=FALSE, Citric_Acid}
qplot(data = df,
      x = citric.acid,
      main = "Red Wines by Citric Acid",
      xlab = "Citric Acid (g / dm^3)",
      ylab = "Count")

citric.acid <-
  ggplot(data = df2,
         aes(x = citric.acid)) +
    geom_histogram() +
    labs(title = "Red Wines by Citric Acid",
         x = "Citric Acid (g / dm^3)",
         y = "Count")

citric.acid_log10 <-
  ggplot(data = df2,
         aes(x = citric.acid)) +
    geom_histogram() +
    labs(title = "Red Wines by Citric Acid (log10)",
         x = "Citric Acid (g / dm^3)",
         y = "Count") +
  scale_x_log10()

grid.arrange(citric.acid, citric.acid_log10, ncol = 1)
```

Citric acid levels in red wine are skewed left with an average level of 0.27.

```{r echo=FALSE, message=FALSE, warning=FALSE, Volatile_Acidity}
ggplot(data = df2,
       aes(x = volatile.acidity)) +
  geom_histogram() +
  labs(title = "Red Wines by Volatile Acidity",
       x = "Volatile Acidity (acetic acid = g / dm^3)",
       y = "Count")
```

The volatile acidity of red wine is normally distributed with a slight left
skew. The average here is 0.53.

```{r echo=FALSE, message=FALSE, warning=FALSE, Fixed_Acidity}
qplot(data = df,
      x = fixed.acidity,
      main = "Red Wines by Fixed Acidity",
      xlab = "Fixed Acidity (tartaric acid = g / dm^3)",
      ylab = "Count")

fixed.acidity <-
  ggplot(data = df2,
         aes(x = fixed.acidity)) +
    geom_histogram() +
    labs(title = "Red Wines by Fixed Acidity",
         x = "Fixed Acidity (tartaric acid = g / dm^3)",
         y = "Count")

fixed.acidity_log10 <-
  ggplot(data = df2,
         aes(x = fixed.acidity)) +
    geom_histogram() +
    labs(title = "Red Wines by Fixed Acidity (log10)",
         x = "Fixed Acidity (tartaric acid = g / dm^3)",
         y = "Count") +
  scale_x_log10()

grid.arrange(fixed.acidity, fixed.acidity_log10, ncol = 1)
```

And finally, the fixed acidity of red wine is skewed left with an average value
of 8.32.

# Univariate Analysis

### What is the structure of your dataset?
There are 12 data points collected on 1599 observations of red wine. The data
is tidy; I came accross no missing values while calculating averages.

### What are the main features of interest in your dataset?
All of the data points are scientifically observable with the exception of
quality. This allows us to compare the chemical properties against the quality
rating to deduce the properties of desirable wine.

### Did you create any new variables from existing variables in the dataset?
No. The data set has a good number of variables already, and creating more would
require an advanced investigation into wine making that goes outside the scope
of what I am trying to achieve.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
Most of the data has some pretty clear outliers. I trimmed the highest 1% of
values from most of the variables, bringing the number of observations down from
1599 to 1470. I also dropped the x column as it only served to uniquely identify
each bottle of wine, which is not important in this investigation.


# Bivariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Pair_Plot}
ggcorr(data = df2,
       method = c("all.obs", "spearman"),
       nbreaks = 4,
       palette = "PuOr",
       label = TRUE,
       name = "Spearman Correlation Coeff.(rho)",
       hjust = 0.8,
       angle = -45,
       size = 2) +
  ggtitle("Spearman Correlation Coefficient Matrix")
```

First, we'll look at a paired plot of all the data. There really isn't anything
here that we would call a strong correlation, although there are a few moderate
ones.

```{r echo=FALSE, message=FALSE, warning=FALSE, Plots_by_Quality}
quality_alcohol <-
ggplot(df2,
       aes(x = quality, y = alcohol, group = quality)) +
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "blue") +
  labs(main = "Bivariate Analysis of Quality and Alcohol",
       x = "Quality",
       y = "Alcohol (% by volume)")

quality_volatile.acidity <-
ggplot(df2,
       aes(x = quality, y = volatile.acidity, group = quality)) +
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "blue") +
  labs(main = "Bivariate Analysis of Quality and Volatile Acidity",
       x = "Quality",
       y = "Volatile Acidity (acetic acid - g / dm^3")

quality_sulphates <-
ggplot(df2,
       aes(x = quality, y = sulphates, group = quality)) +
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "blue") +
  labs(main = "Bivariate Analysis of Quality and Sulphates",
       x = "Quality",
       y = "Sulphates (potassium sulphate - g / dm3")

grid.arrange(quality_alcohol,
             quality_volatile.acidity,
             quality_sulphates,
             nrow = 1)
```

Alcohol has the highest correlation with quality at 0.49. We can see here that
there is a relationship between them, although we would be hard pressed to call
a correlation of 0.49 strong. The correlations with volatile acidity and
sulphates are large enough to be noticed inthis dataset, but can only really be
called weak at best.

Since finding a highly correlated relationship to quality seems to be a bust, we
should take the time to examine other relationships in the dataset. We'll start
with alcohol since it has the strongest positive correlation with quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Plots_by_Alcohol}
ggplot(df2,
       aes(x = alcohol, y = density)) +
  geom_point() +
  stat_smooth(geom="smooth", color = "blue") +
  labs(title = "Relationship Between Alcohol and Density",
       x = "Alcohol",
       y = "Density (g / cm^3)")
```

Alcohol only has one other interesting correlation. A high alcohol content is
associated with a lower density.

Before we end this stage of our investigation, we'll take a look at a variable
with several interesting correlations:

```{r echo=FALSE, message=FALSE, warning=FALSE, Plots_by_Fixed_Acidity}
fixed.acidity_citric.acid <-
ggplot(df2,
       aes(x = fixed.acidity, y = citric.acid)) +
  geom_jitter(alpha = 0.3) +
  stat_smooth(geom = "smooth", color = "blue") +
  labs(x = "Fixed Acidity (tartaric acid - g / dm^3)",
       y = "Citric Acid (g / dm^3)") +
  theme(axis.title = element_text(size = 8))

fixed.acidity_density <-
ggplot(df2,
       aes(x = fixed.acidity, y = density)) +
  geom_jitter(alpha = 0.3) +
  stat_smooth(geom = "smooth", color = "blue") +
  labs(x = "Fixed Acidity (tartaric acid - g / dm^3)",
       y = "Density (g / cm^3)") +
  theme(axis.title = element_text(size = 8))

fixed.acidity_pH <-
ggplot(df2,
       aes(x = fixed.acidity, y = pH)) +
  geom_jitter(alpha = 0.3) +
  stat_smooth(geom = "smooth", color = "blue") +
  labs(x = "Fixed Acidity (tartaric acid - g / dm^3)",
       y = "pH") +
  theme(axis.title = element_text(size = 8))

grid.arrange(fixed.acidity_citric.acid,
             fixed.acidity_density,
             fixed.acidity_pH,
             nrow = 1)
```

These relationships are almost high enough to be considered strong, but we will
err on the side of caution and say they are moderate. Of most interest to me is
the fact that the relationship between fixed acidity and pH is not strong; it
makes sense that the relationship would be negative, since a lower pH value
means higher acidity, but since pH is a measure of acidity I would assume the
relationship would be stronger.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the features of interest vary with other features in \
the dataset?
I had assumed that there would be some features of wine that would stand out as
being indicative of quality. Interestingly, there were no strong relationships,
and the only moderate correlation to quality was alcohol content.

The most notable relationships were fixed acidity to citric acid, density, and
pH and citric acid to fixed acidity, volatile acidity, and pH. Together, they
form a cluster of relationships that seem interesting for future investigation.

### What was the strongest relationship you found?
The strongest relationship was between pH level and fixed acidity with a
correlation of -0.69. This makes sense, since pH is a measure of acidity, and
the lower the pH, the higher the acidity.

# Multivariate Plots Section
For this stage of our investigation, I would like to create some advanced plots
that might show some potentially hidden relationships with quality. We'll start
with a plot of alcohol, density, and quality since this is the strongest chain
of relationships we have to quality.

```{r echo=FALSE, message=FALSE, warning=FALSE, Alcohol_Density_Quality}
quality_alcohol_density <- 
ggplot(data = df2,
       aes(x = alcohol, y = density)) +
  geom_jitter(aes(color = factor(quality)), alpha = 0.7) +
  stat_ellipse(aes(x = alcohol, y = density,
                   group = factor(quality), color = factor(quality))) +
  stat_smooth(method = "lm", col = "white") +
  labs(title = "Relationship Between Quality, Alcohol, and Density",
       x = "Alcohol (% by volume)",
       y = "Density (g / cm^3)") +
  scale_color_brewer(type = "seq",
                     palette = 4,
                     guide = guide_legend(title = "Quality Levels")) +
  theme_dark()

quality_alcohol_density
```

We can see that the groupings by quality trend toward lower density and higher
alcohol levels. It is interesting to note that red wines at the bottom of the
quality spectrum have the most atypical grouping.

I would also like to create a regression model to show the relationship between
quality, alcohol, and density:

```{r echo=FALSE, Quality_Alcohol_Regression_Model}
model <- lm(data = df2,
            formula = quality ~ alcohol + density)

coef(model)
summary(model)

t.test(x = df2$quality, y = c(df2$alcohol, df2$density), alternative = "less")
```

This is very interesting. Creating a linear model from the data, we see that
alcohol and density have a p-score of 0.24, well within our confidence interval.
Accordingly, we would have to reject our null hypothesis and conclue that they
are significant factors in red wine quality. Why is this? We'll come back to
this issue more in the summary.

Since alcohol seems to be the largest factor in quality, let's take a look at
alcohol and quality in relation to some other variables:

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots}
quality_alcohol_volatile.acidity <-
ggplot(data = df2,
       aes(x = alcohol, y = volatile.acidity)) +
  geom_jitter(aes(color = factor(quality)), alpha = 0.6) +
  stat_ellipse(aes(x = alcohol, y = volatile.acidity,
                   group = factor(quality), color = factor(quality))) +
  labs(title = "Red Wine by Alcohol, Volatile Acidity, and Quality",
       x = "Alcohol (% by volume)",
       y = "Volatile Acidity (acetic acid - g / dm^3)") +
  scale_color_brewer(type = "seq",
                     palette = 4,
                     guide = guide_legend(title = "Quality Levels")) +
  theme_dark()

quality_alcohol_sulphates <- 
ggplot(data = df2,
       aes(x = alcohol, y = sulphates)) +
  geom_jitter(aes(color = factor(quality)), alpha = 0.6) +
  stat_ellipse(aes(x = alcohol, y = sulphates,
                   group = factor(quality), color = factor(quality))) +
  labs(title = "Red Wine by Alcohol, Sulphates, and Quality",
       x = "Alcohol (% by volume)",
       y = "Sulphates (potassium sulphate - g / dm3)") +
  scale_color_brewer(type = "seq",
                     palette = 4,
                     guide = guide_legend(title = "Quality Levels")) +
  theme_dark()

quality_alcohol_total.sulfur.dioxide <-
  ggplot(data = df2,
         aes(x = alcohol, y = total.sulfur.dioxide)) +
  geom_jitter(aes(color = factor(quality)), alpha = 0.6) +
  stat_ellipse(aes(x = alcohol, y = total.sulfur.dioxide,
                   group = factor(quality), color = factor(quality))) +
  labs(title = "Red Wine by Alcohol, Total Sulfur Dioxide, and Quality",
       x = "Alcohol (% by volume)",
       y = "Total Sulfur Dioxide (mg / dm^3)") +
  scale_color_brewer(type = "seq",
                     palette = 4,
                     guide = guide_legend(title = "Quality Levels")) +
  theme_dark()

quality_alcohol_citric.acid <-
  ggplot(data = df2,
         aes(x = alcohol, y = citric.acid)) +
  geom_jitter(aes(color = factor(quality)), alpha = 0.6) +
  stat_ellipse(aes(x = alcohol, y = citric.acid,
                   group = factor(quality), color = factor(quality))) +
  labs(title = "Red Wine by Alcohol, Citric Acid, and Quality",
       x = "Alcohol (% by volume)",
       y = "Citric Acid (g / dm^3)") +
  scale_color_brewer(type = "seq",
                     palette = 4,
                     guide = guide_legend(title = "Quality Levels")) +
  theme_dark()

  
quality_alcohol_volatile.acidity
quality_alcohol_sulphates
quality_alcohol_total.sulfur.dioxide
quality_alcohol_citric.acid


```

We will examine the relationships between these further in the next section.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?
The multivariate analysis of this dataset was crucial. Looking at only the
correlation values for the data, we might conclude that the correlations are too
low to show any real relationship. However, our multivariate analysis showed
that this clearly was not the case, and fitting the data to a linear model
proved this.

### Were there any interesting or surprising interactions between features?
Despite alcohol having the strongest correlation to quality (0.49) and density
having a weaker correlation (-0.2), our linear model showed that density also
has a role to play in quality. When looking at the correlation between alcohol
and density (-0.5), we can see that this makes sense.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.
The strength of my model is that it uses a chain of three variables with
reasonably high correlations to show a powerful relationship. It could be made
stronger by taking other variables more directly correlated with quality and
seeing how powerful their effect is.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, message=FALSE, warning=FALSE,  Plot_One}
quality_alcohol
```

### Description One
The bivariate analysis of quality against alcohol is one of my favorites.
Alcohol is far and away the highest correlated value to quality and it brings up
many questions, enough that we could conduct an entirely new investigation. It
is commonly believed that alcohol tastes bad, and the more like alcohol
something tastes, the worse we think of it. Many drinks with high alcohol
content are diluted to avoid the flavor; in fact, wine is one of the few
drinks that is generally not diluted. Do wine drinkers enjoy the taste of
alcohol? Are the testers who gaves these ratings biased towards highly alcoholic
drinks? Does a high alcohol by volume mean that a tester will be in a better
moood when it comes time to rate for quality?

### Plot Two
```{r echo=FALSE, message=FALSE, warning=FALSE,  Plot_Two}
grid.arrange(quality_alcohol_volatile.acidity,
             quality_alcohol_citric.acid,
             nrow = 1)
```

### Description Two
These two plots in conjunction tell an interesting story. Higher quality wines
tend to not only have more alcohol, but also lower volatile acidity and higher
citric acid. This seems to imply that there are different kinds of acidity and
they work quite differently. I would want to do more research before drawing
conclusions, but it seems as though volatile acidity might indicate a more
"vinegary" wine, while higher citric acid indicates more fruit flavors.

### Plot Three
```{r echo=FALSE, message=FALSE, warning=FALSE,  Plot_Three}
quality_alcohol_density
```

### Description Three
This chart is my favorite due to the lesson it teaches about correlation and
p-value. At first glance, it looks like low correlations across the board means
that none of our values significantly impact quality. However, when we create a
linear model comparing alcohol and density to quality, we find an entirely
different story. Not only does alcohol have a relationship to quality with a 
p-value of practically 0, but we find that density has a large impact as well by
way of alcohol: density negatively impacts alcohol, which positively impacts
quality.

------

# Reflection

This analysis was underwhelming at first. I expected to rush in, find some
interesting insights, and zoom off and away to the next project. Instead, I
discovered over ten variables that did not correlate well with quality, leading
me to think that there were no good indicators for what made a good red wine.

I almost didn't do a linear model as part of this analysis, but I am very glad
I did. It was frustrating to find out that the regression model didn't match up
well with my correlations. How could something have such a low p-value but have
a correlation of less than 0.5?

When running correlations, you often hear some loose numbers for what makes a
good correlation: a good correlation is 0.6, 0.7 or even 0.9 and above. This
dataset, for the most part, did not include factors with correlations nearly
that high. To make things even more strange, factors that should be obviously
correlated did not score high as well. What's the deal with pH and fixed acidity
have a correlation of -0.68, but pH and volatile.acidity having a correlation of
0.029?

Using this dataset made me question a lot of beliefs I had about what is and is
not relevant or statistically meaningful data. There are ideal values and
thresholds in statistics, but not every dataset will have them.

For future analysis, I would like to focus on the relationship between quality
and alcohol. Does this hold true for other alcoholic beverages? The craft beer
scene is booming right now; are there corollaries between the two? What about
for other kinds of wine, like plum? How do acid levels affect these drinks?